Consistent ecosystem functional response across precipitation extremes in a sagebrush steppe

### 2017-08-15 manuscript/usses_water_ms.Rmd
updates results with new model calculations

Cumulative March-June soil moisture had a weak positive effect on ANPP (mean of $\beta_{1}$ = `r round(betas$mean[8],2)`; Fig. 3), but the effect is associated with high uncertainty, with credible intervals that overlap zero (80\% BCI = `r round(betas$X10.[8],2)`, `r round(betas$X90.[8],2)`; 95\% BCI = `r round(betas$X2.5.[8],2)`, `r round(betas$X97.5.[8],2)`).
Ecosystem functional response was similar among treatments, with treatment level regressions between soil moisture and log(ANPP) having similar intercepts and slopes (Fig. 3A).
There was also no evidence that the treatment effects became more important over time because there was no directional trend in the random year effects (Fig. 4).

Community composition was similar among treatments.
In no year did community composition among treatments not overlap, and they were equally dispersed in all years (Table 1; Fig. 5).
Likewise, community composition was remarkably stable over time, with no evidence of divergence among treatments (Table 1; Fig. 5).

>>>>

Cumulative March-June soil moisture had a weak positive effect on ANPP (Table 1; Fig. 3), but the effect is associated with high uncertainty, with credible intervals that overlap zero (Table 1).
Ecosystem functional response was similar among treatments (Table 1; Fig. 3), but there is evidence that the slope for the irrigation treatment is less than the slope for the control treatment.
This evidence comes from interpreting the posterior distribution of the slope offset for the irrigation treatment, from which we calculate a 98% probability that the estimate is less than zero (Fig. 3A, right panel).
There was no evidence that the treatment effects became more important over time because there was no directional trend in the random year effects (Fig. A2-2).

Community composition was similar among treatments.
In no year did community composition among treatments not overlap, and they were equally dispersed in all years (Table 2; Fig. 5).
Likewise, community composition was remarkably stable over time, with no evidence of divergence among treatments (Table 2; Fig. 5).

### 2017-08-15 manuscript/usses_water_ms.tex
updates results with new model calculations

Cumulative March-June soil moisture had a weak positive effect on ANPP
(mean of \(\beta_{1}\) = 0.41; Fig. 3), but the effect is associated
with high uncertainty, with credible intervals that overlap zero (80\%
BCI = -0.08, 0.86; 95\% BCI = -0.45, 1.13). Ecosystem functional
response was similar among treatments, with treatment level regressions
between soil moisture and log(ANPP) having similar intercepts and slopes
(Fig. 3A). There was also no evidence that the treatment effects became
more important over time because there was no directional trend in the
random year effects (Fig. 4).

Community composition was similar among treatments. In no year did
community composition among treatments not overlap, and they were
equally dispersed in all years (Table 1; Fig. 5). Likewise, community
composition was remarkably stable over time, with no evidence of
divergence among treatments (Table 1; Fig. 5).

>>>>

Cumulative March-June soil moisture had a weak positive effect on ANPP
(Table 1; Fig. 3), but the effect is associated with high uncertainty,
with credible intervals that overlap zero (Table 1). Ecosystem
functional response was similar among treatments (Table 1; Fig. 3), but
there is evidence that the slope for the irrigation treatment is less
than the slope for the control treatment. This evidence comes from
interpreting the posterior distribution of the slope offset for the
irrigation treatment, from which we calculate a 98\% probability that
the estimate is less than zero (Fig. 3A, right panel). There was no
evidence that the treatment effects became more important over time
because there was no directional trend in the random year effects (Fig.
A2-2).

Community composition was similar among treatments. In no year did
community composition among treatments not overlap, and they were
equally dispersed in all years (Table 2; Fig. 5). Likewise, community
composition was remarkably stable over time, with no evidence of
divergence among treatments (Table 2; Fig. 5).
